### 2017-09-15 etc/2017-08-28_VPD_uWUE_notes/explicit.tex
added pierre's comments and GPP notes, now need to add WUE and then code it all up
added WUE to document, now need to code up
forgot to add typo fixes in explicit and formatting consistency change in data_io
everything looks good except for d_gpp
tweaked formulation to break up roe, really makes atm term constant and better to analyze
minor typo in notes
added other derivatives to d_et

\begin{document}
\begin{center}
\large{Using uWUE to remove dependence of ET on GPP}\end{center}

@@

Penman montieth is given by:

\begin{equation}
  ET = \frac{\Delta R + g_a \rho_a c_p D_{s}}{\Delta + \gamma(1 + \frac{g_a}{g_s})}
\end{equation}

@@

\begin{equation}
  ET = \frac{\Delta R + g_a \left( \rho_a c_p D_{s} - \frac{\gamma c_s \sqrt{D_s} L_v P }{\text{LAI } R \; T \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})} \right) }{ \Delta + \gamma}
\end{equation}

@@

\begin{equation}
\frac{\partial \;  ET}{\partial \; D_s} = \frac{g_a}{\Delta + \gamma}   \left( \rho_a c_p - \frac{\gamma c_s L_v  P }{\text{LAI }1.6 \; R\; T \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D_s}}{2 (g_1 + \sqrt{D_s})^2}\right) \right)
\end{equation}

>>>>

\begin{document}
\begin{center}
\large{Using uWUE to analyticaly evaluate VPD effect on WUE, GPP, and ET}\end{center}

@@

Penman montieth is given by:
n
\begin{equation}
  ET = \frac{\Delta R + g_a \rho_a c_p D_{s}}{\Delta + \gamma(1 + \frac{g_a}{g_s})}
\end{equation}

@@

\begin{equation}
  ET = \frac{\Delta R + \frac{g_a\; P}{T} \left( \frac{ c_p D_{s}}{R_{air}} - \frac{\gamma c_s \sqrt{D_s} L_v }{\text{LAI } R* \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})} \right) }{ \Delta + \gamma}
\end{equation}

@@

\begin{equation}
\frac{\partial \;  ET}{\partial \; D_s} = \frac{g_a \; P}{T(\Delta + \gamma)}   \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s L_v  }{\text{LAI }1.6 \; R\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D_s}}{2 (g_1 + \sqrt{D_s})^2}\right) \right)
\end{equation}

Now that we have ET, we can also use uWUE to get GPP:

\begin{equation}
  \frac{ET}{L_v} = \frac{\text{GPP} \cdot \sqrt{D_s}}{  \text{uWUE}}
\end{equation}

Plugging this into Equation (4) gives:

\begin{equation}
  \text{GPP} = \frac{\text{uWUE}\; \Delta R + g_a \left( \text{uWUE}\; \rho_a c_p D_{s} - \frac{\gamma c_s \sqrt{D_s} L_v P }{\text{LAI } R \; T \; 1.6  (1 + \frac{g_1}{\sqrt{D_s}})} \right) }{L_v \; \sqrt{D_s} \left(\Delta + \gamma \right)}
\end{equation}

Taking the derivative w.r.t $D_s$ gives:

\begin{equation}
  \frac{\partial GPP}{\partial D_s} = \frac{1}{2 L_v D_s^{3/2} \left(\Delta + \gamma \right)} \left( -\text{uWUE}\; \Delta R + g_a \text{uWUE}\; \rho_a c_p  D_s - \frac{g_a g_1  \gamma c_s L_v P }{\text{LAI } R \; T \; 1.6 ( 1 + \frac{g_1}{\sqrt{D_s}})^2 } \right)
\end{equation}

We can also solve for WUE, again using uWUE (just make sure units are correct: mol C/mol H$_2$O):

\begin{equation}
\frac{GPP}{ET} = \frac{\text{uWUE}}{\sqrt{D_s}}
\end{equation}

And the derivative:

\begin{equation}
  \frac{\partial \text{WUE}}{\partial D_s} = -\frac{\text{uWUE}}{2 D_s^{3/2}}
\end{equation}

We can also take the derivative with respect to $g_a$, $\Delta$, and $LAI$. First LAI:

\begin{equation}
  \frac{\partial \; ET}{\partial \; \text{LAI}} = \frac{ g_a\; P }{T \left( \Delta + \gamma \right)}  \frac{\gamma c_s \sqrt{D_s} L_v }{\text{LAI$^2$ } R* \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})}
\end{equation}

Now w.r.t. $g_a$:

\begin{equation}
  \frac{\partial \; ET}{\partial \; g_a} = \frac{ P }{T \left( \Delta + \gamma \right)} \left(\frac{c_p D_s}{R_{air}} -  \frac{\gamma c_s \sqrt{D_s} L_v }{\text{LAI } R* \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})}\right)
\end{equation}

Now w.r.t. $\Delta$:

\begin{equation}
\frac{\partial \;  ET}{\partial \Delta} = \frac{\gamma R - \frac{g_a\; P}{T} \left( \frac{ c_p D_{s}}{R_{air}} - \frac{\gamma c_s \sqrt{D_s} L_v }{\text{LAI } R* \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})} \right) }{ (\Delta + \gamma)^2}
\end{equation}
